Conjure: Summoning Proxies from Unused Address Space

### 2019-09-28 paper/paper.tex
Polish layout

\smallskip
\noindent\textbf{Conjure}\enskip
In this paper, we present \scheme, a Refraction
Networking protocol that overcomes these challenges while retaining
TapDance's ISP-friendly deployment requirements\footnote{
We have released the open source implementation of the Conjure client at 
\url{https://github.com/refraction-networking/gotapdance/tree/dark-decoy}.}.
Our key innovation is an architecture that avoids
having to actively participate in client-to-decoy connections.

@@

We introduce the \scheme protocol (Section~\ref{sec:architecture})
and analyze its security, finding that it resists a broader
range of detection attacks than TapDance.
We have implemented \scheme (Section~\ref{sec:implementation})
and deployed it on a 20~Gbps ISP testbed similar to the TapDance
deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
\scheme has reduced complexity and substantially improved performance
(Section~\ref{sec:evaluation}): on average, \scheme has 20\% lower latency,
14\% faster download bandwidth, and over 1400 times faster upload bandwidth.
In addition, \scheme provides significantly
more flexibility than existing Refraction Networking protocols, allowing maintainers to
respond to future censor techniques.
We believe that these advantages
make \scheme a strong choice for future Refraction Networking deployments.

@@

Our deployment model is identical to that of TapDance: we only require a passive
tap at the deploying ISP, and the ability to inject (spoofed) traffic from phantom
hosts.
Furthermore, we assume
asymmetric routing (i.e. that the tap might only see packets from but not to the
client).
However, we assume a stronger threat model for the adversary than
TapDance, as our design resists active attacks.
\looseness=1

@@

We allow the censor access to the client to register and use its own phantom hosts, 
so the system should ensure that these will not reveal the phantom hosts of other users. The
censor can also actively probe addresses that it sees users accessing, and can
employ tools such as ZMap~\cite{zmap13} to scan large network blocks, excepting
large IPv6 prefixes (e.g. a /32 IPv6 prefix contains $2^{96}$ addresses).
\looseness=1

@@

Prior work by Foremski et al.~\cite{foremski2016entropy} has developed models to
generate likely IPv6 addresses from a set of known addresses, useful for
discovering new hosts to scan given known ones. We use their Entropy/IP tool to
analyze the addresses we collected. Figure~\ref{fig:ipentropy} shows the
normalized entropy of each address 4-bit nibble and the total entropy (18.8 out
of 32). Nibbles that were constant across all addresses
(such as the /32 network prefix nibbles) have zero entropy, while those that
equally span the range of values have maximum entropy (normalized to 1). In our
addresses, we observe an entropy of over 75~bits, with more entropy in the later
segments of the address. While not quite the full 96~bits that uniformly random
would produce, this is still a significant amount for phantom hosts to hide in.

@@

\subsection{Probing phantom hosts}
% censors could actively scan phantom hosts...we review how this works for obfs4, OSSH, masked sites individually
Censors may attempt to actively probe suspected phantom hosts to determine if
they are proxies or real hosts. China has been observed using exactly this technique to
discover existing proxies and Tor bridge
nodes~\cite{tor-bridge-blocking-blog,active-probe,ensafi-tor,china-blocking-tor}.
In response to China's active probing, Tor and other circumvention tool developers have developed
\emph{probe-resistant} protocols, such as \texttt{obfs4}~\cite{obfs4}, Obfuscated SSH
(OSSH)~\cite{ossh}, and Shadowsocks~\cite{shadowsocks}. Each of these protocols
require the client to know a special secret distributed alongside the original
proxy address. Without knowledge of this secret, active-probing censors will not
receive any response from these hosts, making it difficult for censors to tell if
a server is a proxy or a non-responsive legitimate host.

@@

\paragraph{Mask sites}
The censor could also attempt to fingerprint a masked site and compare it to a
suspected \scheme application. For instance, if a phantom host IP responds to a
censors' probes
pretending to be \texttt{example.com}, the censor could probe real instances
of \texttt{example.com} on different ports and see how it responds. Then, the
censor can probe the phantom host IP, and see if it responds similarly (e.g. with
the same set of open ports and payloads for certain kinds of probes). To defend
against this, we forward \emph{all} traffic destined to the phantom host to the
masked site, including ports that are not relevant to the proxy application
(e.g. non 443). This ensures that above the TCP layer, we appear to be the mask
site. However, there may be differences in TCP/IP implementations, for instance,
how IP IDs are incremented, or how TCP timestamps are incremented (or supported
at all) that may be different from the mask site. To combat this, we can filter
mask sites by those that have identical TCP/IP stacks to ours, as we use a
common Linux implementation. We also note that this attack only applies when we
use the mask site as an application, and that \scheme can support other
applications (e.g. obfsproxy, WebRTC, etc) that do not have this issue.

>>>>

\smallskip
\noindent\textbf{Conjure}\enskip
In this paper, we present \scheme, a Refraction
Networking protocol that overcomes these challenges while retaining
TapDance's ISP-friendly deployment requirements
Our key innovation is an architecture that avoids
having to actively participate in client-to-decoy connections.

@@

We introduce the \scheme protocol (Section~\ref{sec:architecture})
and analyze its security, finding that it resists a broader
range of detection attacks than TapDance.
We have implemented \scheme (Section~\ref{sec:implementation})
and deployed it on a 20~Gbps ISP testbed similar to the TapDance
deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
\scheme has reduced complexity and substantially improved performance
(Section~\ref{sec:evaluation}): on average, \scheme has 20\% lower latency,
14\% faster download bandwidth, and over 1400 times faster upload bandwidth.
In addition, \scheme is significantly more
flexible than existing Refraction Networking protocols, allowing maintainers to
respond to future censor techniques with greater agility.
We believe that these advantages will
make \scheme a strong choice for future Refraction Networking deployments.

We have released the open source implementation of the Conjure client at 
\url{https://github.com/refraction-networking/gotapdance/tree/dark-decoy}.

@@

Our deployment model is identical to that of TapDance: we only require a passive
tap at the deploying ISP, and the ability to inject (spoofed) traffic from phantom
hosts.
Furthermore, we assume
asymmetric routing (i.e. that the tap might only see packets from but not to the
client).
However, we assume a stronger threat model for the adversary than
TapDance, as our design resists active attacks.

@@

We allow the censor access to the client to register and use its own phantom hosts, 
so the system should ensure that these will not reveal the phantom hosts of other users. The
censor can also actively probe addresses that it sees users accessing, and can
employ tools such as ZMap~\cite{zmap13} to scan large network blocks, excepting
large IPv6 prefixes (e.g. a /32 IPv6 prefix contains $2^{96}$ addresses).

@@

Prior work by Foremski et al.~\cite{foremski2016entropy} has developed models to
generate likely IPv6 addresses from a set of known addresses, useful for
discovering new hosts to scan given known ones. We use their Entropy/IP tool to
analyze the addresses we collected. Figure~\ref{fig:ipentropy} shows the
normalized entropy of each address 4-bit nibble and the total entropy (18.8 out
of 32). Nibbles that were constant across all addresses
(such as the /32 network prefix nibbles) have zero entropy, while those that
equally span the range of values have maximum entropy (normalized to 1). In our
addresses, we observe an entropy of over 75~bits, with more entropy in the later
segments of the address. While not quite the full 96~bits that uniformly random
would produce, this is still a significant amount for phantom hosts to hide in.
\looseness=-1

@@

\subsection{Probing phantom hosts}
% censors could actively scan phantom hosts...we review how this works for obfs4, OSSH, masked sites individually
Censors may attempt to actively probe suspected phantom hosts to determine if
they are proxies or real hosts. China has been observed using exactly this technique to
discover existing proxies and Tor bridge
nodes~\cite{tor-bridge-blocking-blog,active-probe,ensafi-tor,china-blocking-tor}.
In response to China's active probing, Tor and other circumvention tool developers have developed
\emph{probe-resistant} protocols, such as \texttt{obfs4}~\cite{obfs4}, Obfuscated SSH
(OSSH)~\cite{ossh}, and Shadowsocks~\cite{shadowsocks}. Each of these protocols
require the client to know a secret distributed alongside the original
proxy address. Without knowledge of this secret, active-probing censors will not
receive any response from these hosts, making it difficult for censors to tell if
a server is a proxy or a non-responsive legitimate host.

@@

\paragraph{Mask sites}
The censor could also attempt to fingerprint a masked site and compare it to a
suspected \scheme application. For instance, if a phantom host IP responds to a
censors' probes
pretending to be \texttt{example.com}, the censor could probe real instances
of \texttt{example.com} on different ports and see how it responds. Then, the
censor can probe the phantom host IP, and see if it responds similarly (e.g. with
the same set of open ports and payloads for certain kinds of probes). To defend
against this, we forward \emph{all} traffic destined to the phantom host to the
masked site, including ports that are not relevant to the proxy application
(e.g. non 443). This ensures that above the TCP layer, we appear to be the mask
site. However, there may be differences in TCP/IP implementations, for instance,
how IP IDs are incremented, or how TCP timestamps are incremented (or supported
at all) that may be different from the mask site. To combat this, we can filter
mask sites by those that have identical TCP/IP stacks to ours, as we use a
common Linux implementation. We also note that this attack only applies when we
use the mask site as an application, and that \scheme can support other
applications (e.g. obfsproxy, WebRTC, etc) that do not have this issue.
\looseness=-1
